### 2013-01-15 edupar-13/intro.tex
Write related work

>>>>

In comparison with other educational kernels,
% such as Pintos~\cite{pintos} and Xv6~\cite{xv6},
Pebbles allows students to design and implement their systems ``from the ground up''.
At MIT, students study Xv6~\cite{xv6}, a kernel for multiprocessor x86 machines,
and build their own in a series of labs.
At Stanford, students build kernels following the Pintos architecture~\cite{pintos}.
Both courses supply students with starter code, in which thread lifecycle, stack management, and synchronization primitives are already implemented.
In 15-410, we give starter code only for the machine boot sequence and for dynamic memory allocation, leaving students to design threading and scheduling primitives from scratch.
